Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2020-01-05 write_up/reviewer_response.tex

\\
It would be helpful to have explanation of thermal tolerance earlier than line
155 & We have now added a sentence at the beginning of the section that reads
``[described by a set of probabilities] which are affected by the suitability of

@@

\\
Line 376: What does "Visualized using Gerritsen (2014)" mean? & This was poorly
worded. In hindsight, this should also been in the caption of Figure 5, where
we've now added: ``The figure shows catch composition at each spatial unit

@@

represented by a square pie chart of the four populations. The area of each
colour is proportionate to the weight of each population caught in that unit.
Figure produced with the R package 'mapplots' (Gerritsen et al 2014)." \\

@@

(as a square pie chart) - we've clarified this in the figure caption. \\
\\
Figure 6: Add what the different colors mean to the legend & This is already
included as the legend shows which population is represented by which colour. \\

@@

		\hline

	\textbf{Small issues} &  \\
\\
Line 14 - 18: This phrase is too long and hard to understand. Please, rephrase
this in shorter sentences to clarify this idea. & \\
\\
Lines 20 - 43: These two paragraphs seem redundant.  & \\
\\
Line 68 - 72: The authors mentioned that the MixFishSim could be used to infer
if fisheries data are the real community structure. I suggest adding one or two
phrases to explain how the model could help in this. & We explain that as our
community structure is simulated and therefore known, by comparing our inferred
community structure from commercial catches with our known true structure we
can understand how biases introduced by using commercial fishing as a sample
effects our understanding. We believe this point is adequately covered as
currently written.\\
\\
Line 90. The authors presented the time-step of each module, except the
Recruitment dynamics. The recruitment dynamics probably follow the population
dynamic, but it would be interesting present this explicitly. & Recruitment
occurs along with other population dynamics, but only during defined periods
for each population. We've clarified by saying ``Population dynamics operate on
a daily time-step \textit{(with recruitment occurring only during defined
	seasons for each population),} while.." \\
\\
Line 282: How these population parameters were selected? Randomly? Using real
data? Or the authors only created them? & The demographics were defined by the
authors to broadly reflect a four-species assemblage found in a typical
demersal fishery. We have clarified by including the sentence:  ``The population
demographics were defined to broadly represent three mobile low-medium value
groundfish species and one high value species with low mobility, with the
dynamics hypothetical but as you might expect to find in a typical demersal
fishery." \\ 
\\ 
Line 426: What does adapted means in this context? Exploring
new opened areas?
& Yes, we have clarified in the text that ``the fisheries "adapted" to the
closures textit{by fishing new areas of high abundance to fish}\\
\\
Line 613: Do not use parenthesis inside of other parenthesis. & We have changed
from ``( e.g." to ``, e.g." to eliminate one set of parenthesis. \\
\\
Table 2 and table 3 are not cited in the text Citation of the supplementary
figures are out of order & This is now corrected with references inserted for
Table 2 and 3 and the supplementary figures reorded. \\
\\
Figure 3: Individual years ARE the light grey lines    & Thanks! Corrected. \\
\\
Figure 4. What do the purple spots represent? Describe these spots in the
capture & This has been clarified to be the revenue at each location (darker
the area, higher the revenue). \\
\\
Figure 7. Add what ``res"  means in the caption.  & Have clarified in the
legend text that it means ``resolution" \\
\\
Figure 8. What F means? & Changed to read ``Fishing mortality" \\
\\
		\bottomrule
	\end{longtable}

### 2020-01-10 write_up/mixfishsim_ecolmod_revisions.tex
Changed title
updated abstract

\begin{frontmatter}
\title{Working title: Highly resolved spatiotemporal simulations for
	exploring mixed fishery dynamics}

@@

%%
To understand how data resolution impacts inference on mixed fisheries
interactions we developed a highly resolved spatiotemporal discrete-event
simulation model ('MixFishSim`) incorporating: i) delay-difference population
dynamics, ii) population movement using Gaussian Random Fields to simulate
patchy, heterogeneously distributed populations, and iii) fishery dynamics for
multiple fleet characteristics based on population targeting under an
explore-exploit strategy. This is implemented via a mix of correlated random
walk movement (for exploration) and learned behaviour (for exploitation) phases
of the fisheries. \\ 
%%
Fifty years of sub-daily fishing activity was simulated and used to draw
inference on the underlying community structures. We compared inferences based
on: commercial catch, a simulated fixed-site sampling survey design and the
true \added{(simulated)} underlying populations. We i) establish the potential
limitations of fishery-dependent data in providing a robust picture of
spatiotemporal distributions; and then ii) simulated an area closure based on
areas defined from the different data sources at a range of temporal and
spatial resolutions.\\
%%
Our framework allows users to explore the assumptions in modelling
observational data and evaluate the underlying dynamics of such approaches at a
fine spatial and temporal scale. In application to a mixed fishery exploiting
four different populations we found different spatial patterns were evident and
that the effectiveness of the spatial closure reduced when data were aggregated
across larger spatial areas. However, aggregation across time periods has less
of a negative impact on the closure success and while not as effective as when
based on on the true population, closures based on high catch rates observed in
commercial data could still reduce fishing on a protected species. \\

We conclude from our example framework application that commercial data, while
containing bias, provide a useful tool for managing catches in mixed fisheries
if applied at the correct spatiotemporal scale. \\
%%
\end{abstract}

\begin{keyword}
spatiotemporal \sep mixed fisheries \sep individual based \sep spatial
management \sep heterogeneity \sep  preferential sampling
\MSC[2010] 00-01\sep  99-00
\end{keyword}

@@

In most cases the fishery closure was successful in reducing fishing mortality
on the species of interest (population 3; Figure \ref{fig:3}), though
interestingly the largest reductions in fishing mortality happened immediately
after the closures, following which the fisheries ``adapted" to the closures
\added{by finding new areas of high abundance to fish} and fishing mortality
increased again somewhat. The exception to the success was the closures
implemented based on the coarsest spatial (20 x 20) and temporal resolution
(yearly) that was ineffective (i.e. failed to reduce fishing mortality) with
all data sources. As expected, closures based on the ``known" population
distribution were most effective, with differing degrees of success using the
commercial data. Fishing mortality rates on the other species changed in
different proportions, depending on whether the displaced fishing effort moved
to areas where the populations were found in greater or lesser density. \\

>>>>

\begin{frontmatter}
\title{Highly resolved spatiotemporal simulations for
	exploring mixed fishery dynamics}

@@

%%
To understand how data resolution impacts inference on mixed fisheries
interactions we developed a highly resolved spatiotemporal discrete-event
simulation model ('MixFishSim`) incorporating: i) delay-difference population
dynamics, ii) population movement using Gaussian Random Fields to simulate
patchy, heterogeneously distributed \added{and moving fish} populations, and
iii) fishery dynamics for multiple fleet characteristics based on population
targeting under an explore-exploit strategy.\deleted{ This is implemented via a mix of
correlated random walk movement (for exploration) and learned behaviour (for
exploitation) phases of the fisheries. }\\ 
%%
\deleted{Fifty years of sub-daily fishing activity was simulated and used to
	draw inference on the underlying community structures. W}\added{We
	applied the framework to draw}\deleted{compared} inference\deleted{s}
\added{on community structure} \added{when using data generated from
}\deleted{based on}: commercial catch, a simulated fixed-site sampling survey
design and the true \added{(simulated)} underlying populations.
\deleted{W}\added{In doing so w}e \deleted{i)}establish the potential
limitations of fishery-dependent data in providing a robust picture of
spatiotemporal distributions\deleted{; and then ii) simulated an area closure
	based on areas defined from the different data sources at a range of
	temporal and spatial resolutions.}\deleted{Our framework allows users
	to explore the assumptions in modelling observational data and evaluate
	the underlying dynamics of such approaches at a fine spatial and
	temporal scale. In application to a mixed fishery exploiting four
	different populations w} \added{W}e found different spatial patterns
were evident and that the effectiveness of the spatial closure reduced when
data were aggregated across larger spatial areas. \deleted{; and then
	ii)}\added{We then simulated an area closure based on areas defined
	from the different data sources at a range of temporal and spatial
	resolutions.} Aggregation across time periods has less of a negative
impact on the closure success than over space.\deleted{ and w}\added{W}hile not
as effective as when based on on the true population, closures based on high
catch rates observed in commercial data were still able to reduce fishing on a
protected species. \\

\added{Our framework allows users to explore the assumptions in modelling
	observational data and evaluate the underlying dynamics of such
	approaches at a fine spatial and temporal scale. }\added{From our
	application w}\deleted{W}e conclude that commercial data, while
containing bias, provide a useful tool for managing catches in mixed fisheries
if applied at the correct spatiotemporal scale. \\
%%
\end{abstract}

\begin{keyword}
spatiotemporal \sep mixed fisheries \sep individual based \sep spatial
management \sep heterogeneity \sep bycatch avoidance 
\MSC[2010] 00-01\sep  99-00
\end{keyword}

@@

In most cases the fishery closure was successful in reducing fishing mortality
on the species of interest (population 3; Figure \ref{fig:3}). Interestingly
the largest reductions in fishing mortality happened immediately after the
closures, following which the fisheries ``adapted" to the closures \added{by
	finding new areas of high abundance to fish which led to} fishing
mortality increasing again, though not to past levels. The exception to the
success was the closures implemented based on the coarsest spatial (20 x 20)
and temporal resolution (yearly) that was ineffective (i.e. failed to reduce
fishing mortality) with all data sources. As expected, closures based on the
``known" population distribution were most effective, with differing degrees of
success using the commercial data. Fishing mortality rates on the other species
changed in different proportions, depending on whether the displaced fishing
effort moved to areas where the populations were found in greater or lesser
density. \\
